---
title: 'Lab 7: Multiple Linear Regression Intro'
author: "Van Gonzales"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
```


##Explore Penguins

Use `GGALLY::ggpairs()` to create a pairs plot
```{r}
ggpairs(penguins)
```

Thats kind of overkill so let's simplify the variables that we include in our ggpairs plot:

- species
- bill_length_mm through body_mass_g

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple Linear Regression

We are going to try to understand a bit better, the relationships between multiple predictor variables and an outcome which is penguin body mass.

The different predictor variables we're going to try are:

- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based on only flipper length and bill depth (bad idea, there are important variables missing)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)
#Call model by name to return only coefficients
model_1

# More info on the coefficients 
summary(model_1)
```

If everything else is held constant, we expect that for each 1 mm increase in flipper length, penguin body mass is expected to increase by 51.54 g, on average.
The multiple R-squared  value menas that, 76.1% of the variance in penguin body mass is described by penguin flipper length and bill depth (the model).

Actually we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex.

```{r}
model_2 <- lm(body_mass_g ~ species + flipper_length_mm + sex, data = penguins)

# Lets check out the coefficients

model_2

#Try interpreting the coefficients for:
#flipper length, Gentoo, male
```

The reference levels are female and species adelie.
On average we expect a Gentoo penguin to be 836.26 g larger than an adelie if everything else about them is the same.
On average we expect a male penguin to be 530.38 g larger than a female if everything else about them is the same

## Visulaize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species)) +
  facet_wrap(~sex)
```

## Acouple ways to get & report MLR modle outcomes

Use broom::tidy() to get model coefficient info in a tidy data frame

```{r}
penguin_model_2_coef <- tidy(model_2)

penguin_model_2_coef
```

Try to write inline code 1r1 that spits out the coefficient for Gentoo.
`r penguin_model_2_coef$estimate[3]`.

## Look at model diagnostics

Use plot() function.

```{r}
plot(model_2)

summary(model_2)
```

## Report the model outputs in a summary table

Use modelsummary:
```{r}
modelsummary(model_2)
```

Use stargazer:
```{r, results = "asis"}
stargazer(model_2, type = "html")
```

